\datedsubsection{Mar. 2023 -- Present}
{Freelance Full Stack Developer}
{\textbf{Independent \& Fractal}}
{
    \begin{itemize}
        \item Worked as a freelance full-stack web developer to support my
              college education, securing projects independently on
              \href{https://www.upwork.com/freelancers/~015388e15d840b96cb}{Upwork}
              and through \href{https://fractalweb.netlify.app/}{Fractal}, a freelance
              agency I co-founded.
        \item Developed a range of internal business
              applications, e-commerce platforms, and designed digital media for
              brand communication, utilizing diverse web technologies and
              frameworks like Flutter, NextJS, Python (Tkinter, Selenium,
              Pandas), and others.
    \end{itemize}
}
%
%
\datedsubsection{Oct. 2023 -- Apr. 2025}
{Software Developer (Part-time)}
{\textbf{Tagglabs Experimental Pvt. Ltd., Gurgaon}}
{
    \begin{itemize}
        \item Began as an intern and was subsequently retained as a
              part-time/contract software developer after three months, reflecting
              strong early contributions.
        \item Led the development of the alpha release of a cross-platform
              augmented reality, location-aware mobile application using Flutter for
              Android and iOS.
        \item Developed an internal Flutter package for the application,
              integrating the SIFT algorithm for feature matching via native C APIs
              and the OpenCV library.  Used Python's Django library for the back-end
              server of the platform.
    \end{itemize}
}
%
%