\datedsubsectionnarrow{2024}
{}
{\href{https://drive.google.com/file/d/1EF9wtUCJqQINYWiY4uFL4mmktJBL6r1b/view?usp=sharing}{\textbf{Data Analysis and Visualisation with Pandas}}, Course Project}
{
    \begin{itemize}
        \item Worked on a US Housing dataset with the python libraries Seaborn, Pandas and Numpy.
        \item Drew statistical inferences using Violin Plot, Scatter Plot, KDE Plot etc.
        \item Found correlations between various characterisitcs of the US Housing market using basic statistical descriptions.
    \end{itemize}
}
%
%
\datedsubsectionnarrow{2023}
{}
{\href{https://drive.google.com/file/d/13pGjNeMmEKgKJDV8-RHDgqpyPXeEQqEc/view?usp=sharing}{\textbf{Intersectional Analysis of Bama's Sangati}}, Course Project}
{
    \begin{itemize}
        \item An intersectional analysis of a portion of the canonical text in Indian Feminist Literature, Sangati by Bama.
    \end{itemize}
}
%
%
\datedsubsectionnarrow{2021}
{Randomness Challenge}
{\href{https://randomnesschallenge-71zq.onrender.com/}{\textbf{Behavioural and Statistical Experiment}}}
{
    \begin{itemize}
        \item Test the ability of users to be random by asking them to click 6 identical buttons in a random fashion.
        \item Uses different statistical methods to analyse the data collected, uses a REST API to store data in an Object Relational Database.
        \item Made using ExpressJS, ReactJS, Heroku and MongoDB.
    \end{itemize}
}
%
%
\datedsubsectionnarrow{2021}
{Cz Creation Online Shop}
{\href{https://czcreation.onrender.com/}{\textbf{MERN Stack E-commerce Website}}}
{
    \begin{itemize}
        \item A fully fledged e-commerce website for a small business taking their products online.
        \item It has user authentication using JWT tokens, CRUD operations like the ability to add items to cart, place orders, forgot password etc. implemented using a REST API.
        \item Made using MERN stack, hosted on Heroku.
    \end{itemize}
}
\datedsubsectionnarrow{2021}
{Medcheck}
{\href{https://github.com/confumbit/medcheck}{\textbf{Medicine Tracker Android App}}}
{
    \begin{itemize}
        \item An app made using React Native that tracks your medicines for you and warn you whenever a particular medicine is running low.
        \item Made using Expo, React Native, SQLite3.
    \end{itemize}
}
\datedsubsectionnarrow{2020}
{Breeze}
{\href{https://github.com/confumbit/Breeze}{\textbf{Automatic Attendance System using Python and
            Tesseract-OCR}}}
{
    \begin{itemize}
        \item Enables a teacher conducting a class to take attendance effortlessly in Google Meet using the chat.
        \item Made using Python and Tesseract-OCR.
    \end{itemize}
}