\datedsubsectionnarrow{2025}
{}
{\href{https://drive.google.com/file/d/1ccd4o58qntyjndkokzaeszttc6epykrq/view?usp=sharing}
    {\textbf{$p$-adic numbers}}, Supervisor: Mr. B. Sèmthanga}
{
    \begin{itemize}
        \item Studied the p-adic norm and its properties, Ostrowski's Theorem, construction of the field of p-adic numbers and their basic algebra, resulting in a 13-page report.
        \item Presented a talk on the p-adic metric space based on the report.
    \end{itemize}
}

\datedsubsectionnarrow{2024}
{}
{\href{https://drive.google.com/file/d/11-x1EeIfJQ-dBzBWS3uMN9M7creMVBjU/view?usp=sharing}
    {\textbf{Tracing Closed Curves with Epicycles}}, Supervisor: Prof. S. K. Kaushik}
{
    \begin{itemize}
        \item In this paper me and my co-authors introduce the fundamental concepts of Fourier series and transforms (continuous and discrete), going into their mathematical formulations, properties and applications.
        \item Along with it is a python program that performs the discrete Fourier transform to animate closed curves (stored as SVGs) with epicycles.
    \end{itemize}
}

\datedsubsectionnarrow{2023}
{}
{\href{https://drive.google.com/file/d/17TYu954BWVxVPbyHTLwTCE6rcR60hcNU/view?usp=sharing}
    {\textbf{Big-$O$ Notation}}, Supervisor: Prof. S. K. Kaushik}
{
    \begin{itemize}
        \item Explored the mathematical foundations and applications of Big O notation in calculus and computer science, including algorithm complexity and asymptotic analysis.
        \item Emphasized rigorous formal definitions, graphical interpretation, and pedagogical approaches using Landau symbols for error estimation and function growth.
    \end{itemize}
}
